IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-17 paper/appendix.tex
move single heap to appendix

>>>>

\section{IFC Language with a Single Heap}
\label{sec:single-heap}

As a concrete instantiation of this proof technique, we show
how to make implement our IFC language using a single heap and
ensure its non-interference using the techniques presented.
First, we can construct the restricted language
|restrictedLangNoRef alpha targetLangML|, where |noRefs| is
the family of always valid predicates, except for the ones for
\textsc{I-sandbox} and \textsc{I-send}, which we define as
$ P(|ie|) = (\mathcal{AV}(|ie|) = \emptyset{}) $
where $\mathcal{AV}(|ie|)$ denotes the set of address variables in |ie|.
That is, we do not restrict any rules except for \textsc{I-sandbox}
and \textsc{I-send}.
Since $P$ only depends on |ie|, which is part of the current
task and thus never erased w.r.t.\ the label of the first task,
this language satisfies non-interference by Theorem~\ref{thm:restricted}.

\begin{figure}

  \begin{mathpar}
    \inferrule[C-sandbox]
    {
      \mathcal{AV}(|ie|) = \emptyset{}\\
      |iS' = bracket iS (mapsto id' nil)|\\
      |it1 = oneheapfullconf id il (iniE id')|\\
      |itnew = oneheapfullconf id' il (TI ie)|\\
      |fresh id'|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id1 il1 (iniEi (sandbox ie)), ldots)
      .->
      iS'; tS; sched box (it1, ldots, itnew)
    |}
    \and
    \inferrule[C-send]
    {
      \mathcal{AV}(|ie|) = \emptyset{}\\
      |canFlowTo2 il il'|\\
      |iS(id') = Q|\\
      |iS' = bracket iS (mapsto id' (il', id,  iv) , Q)|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id il (iniEi (send id' il' iv)), ldots)
      ->
      iS; tS; sched step (oneheapfullconf id il unit, ldots)
    |}
  \end{mathpar}

  \caption{A selection of the reduction rules for |concreteLangMl alpha|.}
  \label{fig:concrete}
\end{figure}

The essential parts of the semantics for the concrete language
with a single heap,
which we call |concreteLangMl alpha|,
are given in Figure~\ref{fig:concrete}.  Most rules are
straight-forward translations of the rules in Figures~\ref{fig:ifc}
and~\ref{fig:embedding} but for a single heap.  For conciseness, we
only show the interesting ones.
Now, we can show an isomorphism between this language and
|restrictedLangNoRef alpha targetLangML|, which
(by Theorem~\ref{thm:iso-tsni} and~\ref{thm:iso-tini}) guarantees
non-interference for an appropriate scheduling policy |alpha|.

To this end, we represent addresses in the concrete language as
pairs $(|id|,|ta|)$ where |id| is a task identifier, and |ta| an
address in the abstract system\footnote{Note that this does
  not make the isomorphism trivial, as in the single heap, there
  is nothing preventing task 1 to access an address (2,|ta|).
  Furthermore, it is common to represent addresses in this way
  for efficient garbage collection of dead tasks.}.
We also formulate the following well-formedness condition for
configurations:
\[
  |wf c| = \forall |oneheapfullconf id il ie| \in |ic|.\ 
  \{ (|id'|,|ie'|) \in \mathcal{AV}(|ie|) \ \vert\ |id| \neq |id'| \} = \emptyset
\]
Essentially, every address in a given task must have the correct
identifier as the first part of the address.  It is easy to
see that the initial configuration satisfies this condition, and
any step in the concrete semantics preserves the condition.
Therefore, we only need to consider well-formed configurations,
which allows us to give the two required functions
|f| and |finv| for the isomorphism.  For conciseness, we only give
the interesting parts of their definition,
and leave out the straight-forward proof that they
actually provide an isomorphism.
\begin{itemize}
  \item Addresses can be directly translated with
  $|f|((|id|,|ta|))=|ta|$, and $|finv|(|ta|)=|(id,ta)|$ for
  an address |ta| that occurs in task |id|.
  \item |f| splits the single heap into multiple heaps based on
  the |id| of the addresses.  |finv| produces a single heap
  by translating the addresses and collapsing everything to a single
  store.
\end{itemize}
